Selective Sequential Model Selection

### 2015-10-20 paper.tex
some JTcomments

@@

\subsubsection{Ever-Active Regularization Paths and next-$\lambda$ Tests}
Another important class of model selection procedures is the sequence of {\em ever-active} sets for a regularized likelihood path. 
The notion of ever-active sets is needed since these solution paths can drop  (as well as add) predictors along the way. 	For some ordered set $\Lambda$, let $\lambda\in\Lambda$ parameterize the regularization penalty $P_\lambda(\theta)$. In the case of lasso-penalized regression, we could take $P_\lambda = \lambda\|\beta\|_1$ for $\lambda\in (0,\infty]$. 
We assume $P_\lambda(\beta)$  has the property  that the model becomes less constrained as $\lambda$ decreases, that is,
 if $\lambda_2<\lambda_1$ then $\{\beta:P_{\lambda_2}(\beta)\} \supset \{\beta:P_{\lambda_1}(\beta)\}$.  \RTcomment{Will: is this correct?}

@@

@@

The sufficient filtration separates $p_{1:d}$ if and only if 
\begin{enumerate}
\item $p_k$ is conservative given $M_{0:k-1}$ and $U_{k-1}$, and \RTcomment{clearer to say ``sub-uniform''?}
\item $p_k$ is a function of $M_{0:k}$ and $U_k$.
\end{enumerate}

@@

@@

@@

@@

@@

\WFcomment{Can we do this one?}
Here we consider model selection for principal components analysis. In that case we are given a data matrix $X \in \R^{n\times d}$, with which we form a sample %covariance matrix
\[
S = \frac{1}{n-1} \sum_{i=1}^n(x_i - \bar x)^2
\]
The first $d$ principal component loadings are the first $d$ eigenvectors of $S$, which call $u_1,\ldots, u_d$. These induce a sequence of nested Wishart models:
\[
M_0 \sub M_1 \sub \cdots \sub M_d
\]
in which
\begin{equation}
  M_k:\; (n-1) S \sim W_d\left(\lambda_0 I_d + \sum_{i=1}^k     \lambda_i u_i u_i', \;\;\; n-1\right).
\end{equation}
 By successively conditioning on $u_j, j<k$ one can obtain an exact sequential test
for the complete null hypothesis $H_0: \lambda_j=0 \; \forall j \neq k$.  The computation of the resulting $p$-values requires numerical integration.
The details are given in \citet{choi2014selecting}, with their ``integrated CSV'' test  corresponding to the sequential selective test of this paper.

@@

>>>>

\JTcomment{ Not sure if stopping rule is a great name. It suggests it is a ``stopping time'' with respect to some filtration (which it often is). But it doesn't have to be. Or maybe we should say we call it stopping because we use the property of it being a stopping time?

Another notation quibble for $M(E)$ I kind of prefer the notation $(\beta_E, \sigma^2_E)$ instead of $(\beta, \sigma^2)$. It emphasizes that these are parameters of different models.}

@@

\subsubsection{Ever-Active Regularization Paths and next-$\lambda$ Tests}
Another important class of model selection procedures is the sequence of {\em ever-active} sets for a regularized likelihood path. 
The notion of ever-active sets is needed since these solution paths can drop  (as well as add) predictors along the way. 	For some ordered set $\Lambda$, let $\lambda\in\Lambda$ parameterize the regularization penalty $P_\lambda(\theta)$. In the case of lasso-penalized regression, we could take $P_\lambda = \lambda\|\beta\|_1$ for $\lambda\in (0,\infty]$. 
We assume $P_\lambda(\beta)$  has the property  that the model becomes less constrained as $\lambda$ decreases, that is,
 if $\lambda_2<\lambda_1$ then $\{\beta:P_{\lambda_2}(\beta)\} \supset \{\beta:P_{\lambda_1}(\beta)\}$.  \RTcomment{Will: is this correct?} \JTcomment{Yes, this looks a little funny to me too. Not all penalties produce
sparsity (for example, the generalized LASSO). So, I think this section is really thinking 
of $\ell_1$ norm (maybe a group LASSO norm). As written, 
we are also assuming that
there is a unique solution to (11) (which is not a big assumption but we might
as well make it.) Finally, $\ell$ does not actually have to be a likelihood.}

@@

\JTcomment{Maybe a comment about Type I and Type III ANOVA tables here? I think these are the correct types of ANOVA tables but am not sure...This issue of full vs incremental at least has some classical literature on it.}

@@

The sufficient filtration separates $p_{1:d}$ if and only if 
\begin{enumerate}
\item $p_k$ is conservative given $M_{0:k-1}$ and $U_{k-1}$, and \RTcomment{clearer to say ``sub-uniform''?} \JTcomment{I think you mean ``super-uniform'', i.e. it is larger than a uniform random variable?}
\item $p_k$ is a function of $M_{0:k}$ and $U_k$.
\end{enumerate}

@@

\JTcomment{I would say our goal is a good stopping rule AND inference on parameters of selected (or perhaps saturated) model. We do not consider it here
because we don't know how to do it, not because it is not interesting.}

@@

\JTcomment{We actually don't really need to condition on the signs
for the theory to go through. It is only so that sampling is feasible.}

@@

\JTcomment{Is there a reason you have $\psi$ and $\ell$ above instead of just $\ell$? I think the $(E,t)$ above should be $(E,u)$. It seems you never come back to $\psi$.}

@@

\JTcomment{The notation $R_k$ isn't really defined. I don't think you need an
index $r$ and $k$, so we could talk about for every $\lambda \in \Lambda \geq \lambda_k$ instead of every $r \leq R_k$. No?
Here we do use the fact that the objective is a likelihood.}

@@

\WFcomment{Can we do this one?}
\JTcomment{In principle, we can. But, paper is a little long. Maybe
just point out in discussion
that the $p$-values in Choi et al. are examples of this setup?}

Here we consider model selection for principal components analysis. In that case we are given a data matrix $X \in \R^{n\times d}$, with which we form a sample %covariance matrix
\[
S = \frac{1}{n-1} \sum_{i=1}^n(x_i - \bar x)^2
\]
The first $d$ principal component loadings are the first $d$ eigenvectors of $S$, which call $u_1,\ldots, u_d$. These induce a sequence of nested Wishart models:
\[
M_0 \sub M_1 \sub \cdots \sub M_d
\]
in which
\begin{equation}
  M_k:\; (n-1) S \sim W_d\left(\lambda_0 I_d + \sum_{i=1}^k     \lambda_i u_i u_i', \;\;\; n-1\right).
\end{equation}
 By successively conditioning on $u_j, j<k$ one can obtain an exact sequential test
for the complete null hypothesis $H_0: \lambda_j=0 \; \forall j \neq k$.  The computation of the resulting $p$-values requires numerical integration.
The details are given in \citet{choi2014selecting}, with their ``integrated CSV'' test  corresponding to the sequential selective test of this paper.

@@

\JTcomment{Max $T$ available in python code on github. I suppose R as well, but not sure.}
